Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-13 talk/pepm2011/paper.tex
typo

The partial evaluation works by walking the trace from beginning to end.
Whenever a \texttt{new} operation is seen, the operation is removed and a static
object is constructed and associated with the variable that would have stored
the result of \texttt{new}. The static object describes the shape of the
original object, \eg where the values that would be stored in the fields of the
allocated object come from, as well as the type of the object. Whenever the
optimizer sees a \texttt{set} that writes into such an object, that shape
description is updated and the operation can be removed, which means that the
operation was done at partial evaluation time. When the optimizer encounters a
\texttt{get} from such an object, the result is read from the shape
description, and the operation is also removed. Equivalently, a
\texttt{guard\_class} on a variable that has a shape description can be removed
as well, because the shape description stores the type and thus the outcome of
the type check che guard does is statically known.

>>>>

The partial evaluation works by walking the trace from beginning to end.
Whenever a \texttt{new} operation is seen, the operation is removed and a static
object is constructed and associated with the variable that would have stored
the result of \texttt{new}. The static object describes the shape of the
original object, \eg where the values that would be stored in the fields of the
allocated object come from, as well as the type of the object. Whenever the
optimizer sees a \texttt{set} that writes into such an object, that shape
description is updated and the operation can be removed, which means that the
operation was done at partial evaluation time. When the optimizer encounters a
\texttt{get} from such an object, the result is read from the shape
description, and the operation is also removed. Equivalently, a
\texttt{guard\_class} on a variable that has a shape description can be removed
as well, because the shape description stores the type and thus the outcome of
the type check the guard does is statically known.
